\documentclass[main.tex]{subfiles}

\begin{document}
\section{Integration}
\begin{multicols}{2}
	\subsection*{Basics}
	\begin{definition}[integration as antiderivative]
	If \(F(x)\) is an antiderivative of \(f(x)\) s.t. \(F'(x) = f(x)\),
	and the general antiderivative of \(f(x)\) is \(F(x) + C\),
	where \(C \in \R\) is an arbitrary constant of integration,
	then \[\int f(x) \ dx = F(x) + C.\]
	\end{definition}

	\begin{definition}[definite integration via Riemann sums]
	Suppose that \(f(x)\) is continuous within \([a, b]\). Then, by dividing \([a, b]\) into \(n\) subintervals of width \(\Delta x\), picking \(x_i\) for each interval,
	\[\int_{a}^b f(x) \ dx = \lim_{n \to \infty}{\left(\sum_{i = 1}^n f(x_i) \Delta x  \right)}\] (per Riemann sums.)
	\end{definition}

	\subsubsection*{Common finite sums}
	\begin{align*}
	\sum_{i = 1}^n 1 &= n & \sum_{i = 1}^n i &= \frac{n(n + 1)}{2} \\
	\sum_{i = 1}^n i^2 &= \frac{n(n + 1)(2n + 1)}{6} & \sum_{i = 1}^n i^3 &= \frac{n^2(n + 1)^2}{4}
	\end{align*}

	\subsection*{Fundamental theorem of calculus}
	\begin{enumerate}
	\item If \(f(x)\) is continuous on \([a, b]\), then
	\(g(x) = \int_a^b f(t) \ dt\) is also continuous on \([a, b]\) s.t.
	\[g'(x) = \frac{d}{dx} \left(\int_a^b f(t) \ dt \right) = f(x).\]
	\item If \(f(x)\) is continuous on \([a, b]\) and \(F(x) = \int f(x) \ dx\), then
	\[\int_a^b f(x) \ dx = F(b) - F(a).\]
	\end{enumerate}

	\subsection*{Common integrals}
	\subsubsection*{Basics}
	\begin{align*}
	\int \frac{1}{x} \ dx = \ln |x| + C && \int \frac{1}{ax + b} \ dx = \frac{1}{a} \ln |ax + b| + C
	\end{align*}

	\subsubsection*{Trig functions}
	\begin{align*}
		\int \tan{\theta} \ d\theta &= -\ln{|\cos{\theta}|} + C & \int \cot{\theta} \ d\theta &= \ln{|\sin{\theta}|} + C \\
		&= \ln{|\sec{\theta}|} + C & &= -\ln{|\csc{\theta}|} + C
	\end{align*}
	\begin{align*}
		\int \sec{\theta} \ d\theta &= \ln{|\sec{\theta} + \tan{\theta}|} + C \\
		\int \csc{\theta} \ d\theta &= \ln{|\csc{\theta} - \cot{\theta}|} + C
	\end{align*}
	\subsubsection*{Logarithms}
	\begin{align*}
	\int e^x \ dx = e^x + C && \int a^x \ dx = \frac{a^x}{\ln{a}} + C
	\end{align*}

	\subsection*{Integration techniques}
	\subsubsection*{\(u\)-substitution}

	\subsubsection*{Integration by parts}
	\[\int u \ dv = uv - \int v \ du\]
	Make sure that \(\int v \ du\) is somehow simpler than the integrand. The rule of thumb is to choose \(dv\) to be the most complicated part of the integrand but mentally doable. Note that integration by parts is often used as a last-resort.

	\subsubsection*{Products and some quotients of trig functions}
	For \(\displaystyle \int \sin^n{x} \cos^m{x} \ dx\):
	\begin{enumerate}
	\item \(n\) odd: strip 1 sine out, convert the rest to cosines; then use \(u = \cos{x}\).
	\item \(m\) odd: strip 1 cosine out, convert the rest to sines; then use \(u = \sin{x}\).
	\item \(n\) and \(m\) odd: use either 1 or 2
	\item \(n\) and \(m\) even: use double-angle and/or half-angle formula to reduce equation to easily-integrable form.
	\end{enumerate}

	For \(\displaystyle \int \tan^n{x} \sec^m{x} \ dx\):
	\begin{enumerate}
	\item \(n\) odd: strip 1 tan and 1 secant, convert the rest to secants; then use \(u = \sec{x}\).
	\item \(m\) even: strip 2 secants out, convert the rest to tan; then use \(u = \tan{x}\).
	\item \(n\) odd, \(m\) even: use either 1 or 2.
	\item \(n\) even, \(m\) odd: good luck (use a combination of identities, integration by parts, and "ingenuity" (per my notes))
	\end{enumerate}

	For \(\displaystyle \int \sin{ax} \cos{bx} \ dx\), \(\displaystyle \int \sin{ax} \sin{bx} \ dx\), \(\displaystyle \int \cos{ax} \cos{bx} \ dx\): use either the appropriate sum-difference angle formulae or doing integration by parts twice.

	\subsubsection*{Trig substitution}
	\begin{enumerate}
		\item For integrals involving a factor of \(a^2 - x^2\) or \(1 - \frac{x^2}{a^2}\), use trig sub \(x = a \sin{\theta}\)
		\item For integrals involving a factor of \(a^2 + x^2\) or \(1 + \frac{x^2}{a^2}\), use trig sub \(x = a \tan{\theta}\)
		\item For integrals involving a factor of \(x^2 - a^2\) or \(\frac{x^2}{a^2} - 1\), use trig sub \(x = a \sec{\theta}\)
	\end{enumerate}
	
	\subsubsection*{Partial fraction decomposition}
	% copied from slides in MATH 146
	For \(\int \frac{f(x)}{g(x)} \ dx\), do the following:
	\begin{enumerate}
		\item make sure that \(\frac{f(x)}{g(x)}\) is a proper fraction (i.e. \(f(x)\)'s degree is lower than \(g(x)\)). If not, divide \(f(x)\) by \(g(x)\) per long division, and work with the remainder terms.
		\item Factorize \(g(x)\).
		\item Let \(x - r\) be a linear factor of \(g(x)\). Note that \(r\) can be any number. Suppose \((x - r)^m\) is the highest power of \(x - r\) when factoring \(g(x)\). Then, to this factor, assign the sum of the \(m\) partial fractions, i.e. 
		\[\frac{A_1}{(x - r)} + \frac{A_2}{(x - r)^2} + \dots + \frac{A_m}{(x - r)^m}.\] 
		Do this for each distinct linear factors of \(g(x)\).
		\item Let \(x^2 + px + q\) be an \emph{irreducible} quadratic factor of \(g(x)\) (i.e. \(b^2 - 4ac < 0\).) Suppose \((x^2 + px + q)^n\) is the highest power of \(x^2 + px + q\) when factoring \(g(x)\). Then, to this factor: 
		\[\frac{B_1x + C_1}{(x^2 + px + q)} + \frac{B_2x + C_2}{(x^2 + px + q)^2} + \dots + \frac{B_n x + C_n}{(x^2 + px + q)^n}.\]
		Do this for each distinct quadratic factors of g(x).
		\item Write the sum of all these partial fractions as one fraction, and equate it to \(\frac{f(x)}{g(x)}\).
		\item Equate the coefficients of the same powers of \(x\) in the numerators of both sides, and find the coefficients. Then replace them back into the partial fraction form.
	\end{enumerate}

\end{multicols}

\end{document}